\documentclass[modern]{aastex631}
%\documentclass[twocolumn]{aastex631}

\usepackage{hyperref}
\usepackage{color}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{xfrac}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{longtable}
\newcommand{\im}{\color{green}}
\newcommand{\blue}{\color{blue}}
\newcommand{\oii}{[\ion{O}{2}]$\lambda\lambda 3726,3729$ }
\newcommand{\deltachisq}{{\ensuremath{\Delta \chi^2}}}
\newcommand{\snroii}{\ensuremath{{\rm SNR}(F_{\rm O\,II})}}

\graphicspath{{./}{figures/}}

\submitjournal{\aj}

\shorttitle{FastSpecFit}
\shortauthors{Moustakas}

\begin{document}

\title{FastSpecFit: Spectrophotometric Modeling of 3.6 Million Extragalactic Targets from the DESI Early Data Release and Data Release 1} 

\correspondingauthor{John Moustakas}
\email{jmoustakas@siena.edu}

\author[0000-0002-2733-4559]{John Moustakas}
\affil{Department of Physics \& Astronomy, Siena College \\ 515 Loudon Road, Loudonville, NY 12110, USA}

%\author[]{Your Name Here}
%\affil{You Affiliation Here}

\begin{abstract}
The observed-frame optical spectrum of each extragalactic DESI target contains a wealth of information beyond just its redshift. FastSpecFit (https://fastspecfit.readthedocs.io) is open-source software written in Python which has been developed to extract this information by modeling each observed DESI spectrum and its broadband photometry using physically grounded stellar continuum and emission-line templates. The quantities FastSpecFit measures include: light-weighted ages and stellar velocity dispersions based on the underlying stellar continuum; line-widths, velocity shifts, integrated fluxes, and equivalent widths for more than 40 rest-frame ultraviolet, optical, and near-infrared emission lines arising from both star formation and AGN activity; K-corrections and rest-frame absolute magnitudes and colors; and much more. Multiple existing projects are relying on the measurements which are being generated by FastSpecFit. This Project will likely result in multiple papers, including (1) a technical paper which describes the code and demonstrates its performance compared to existing codes; (2) a paper describing the FastSpecFit Value Added Catalog (VAC) associated with the Early Data Release (EDR); and (3) a VAC paper associated with Data Release 1 (DR1).
\end{abstract}

\keywords{Galaxies, Surveys, Catalogs}

\section{Introduction}\label{sec:intro}
Introduce very important papers like \citet{moustakas13a}.

https://ui.adsabs.harvard.edu/abs/2022ApJ...935..167A/abstract

Papers to read and reference:

\begin{enumerate}
\item https://arxiv.org/pdf/2205.04987.pdf
\item 
\end{enumerate}

\section{Data}\label{sec:data}

Positional matching to get DR9 photometry.

Robust continuum-fitting: \url{https://www.aanda.org/articles/aa/pdf/2018/01/aa30425-17.pdf}

Compare with Hu's VAC:

Data: ​https://data.desi.lbl.gov/desi/users/zouhu/vac/edr/ Documentation: ​https://data.desi.lbl.gov/desi/users/zouhu/vac/edr/readme.md

WISE stellar mass calibrations:
https://ui.adsabs.harvard.edu/abs/2023arXiv230105952J/abstract

Compare my [OII] with Anand's emfit results.

Compare with Salim+16 overlapping SDSS galaxies.

Compare with PROVABGS:

Data: ​https://data.desi.lbl.gov/desi/users/chahah/provabgs/edr/ Documentation: ​https://data.desi.lbl.gov/desi/users/chahah/provabgs/edr/readme.md

Compare with Mar's stuff:

/global/cscratch1/sd/msiudek/StMassCatalog/ReadMe.txt


\section{Algorithms}

\subsection{Spectrophotometric Templates}\label{sec:templates}

We use the C3K models from FSPS to build our templates. IMF, isochrones, stellar library. FSPS provides the option of including nebular emission lines in the models, which can be important for computing K-corrections.

The code includes the option of excluding templates which are older than the age of the universe. However, by default we choose to use all models, largely because of the relatively coarse grid in mean age. In future work we will explore this option in more detail.

\subsection{Procedure}

We solve for velocity dispersion only if ((S/N>3 in B or R arm) AND (redshift < 1)).

Figures for this section:
\begin{itemize}
\item Fig which illustrates how we identify significant lines, how we measure EWs, and how we compute upper limits.
\end{itemize}

SPS papers: \citet{johnson21a}, \citet{suess22a}. 

Steps in the fitting:

\begin{itemize}
\item First, estimate the stellar velocity dispersion. In order to estimate the velocity dispersion, we require at least 500~\AA{} of rest-frame wavelength coverage in the spectral range $3500-5500$~\AA. In addition, we normalize the continuum in the templates and the data and we only use templates with $fagn=0$ and $A_V=0$, which have a negligible effect on the stellar absorption lines.

\item The aperture correction may not be perfect for QSOs, but in general our templates have enough flexibility that they can recover the shape of the broadband SED reasonably well.
\end{itemize}

% This magic happens in io.select around line 780.
Special handling of PHOTSYS, which may not match the value in the DESI catalogs for secondary and tertiary targets. First, if PHOTSYS is neither N or S and RELEASE is defined then we use the desitarget release dictionary to determine PHOTSYS. Otherwise we use a declination cut. Either way, all photometry ultimately has N or S, which uniquely associates the photometry with the appropriate filter curves.

The broad-line model can be dropped for three possible reasons: delta-chi2 is > 0.0; all broad-line amplitudes are zero; broad_sigma<broad_narrow.

\section{Results}\label{sec:results}

Aperture bias as a function of properties and redshift.

Should add a nice section of spectrophotometry.

Do a colors as a function of redshift and show that the models match the data well.

Note that H6~$\lambda3890$ may be blended with HeI~$\lambda3889$, so beware.

\section{Discussion \& Summary}\label{sec:summary}

Improvements: 

\begin{itemize}
\item Use NMF to train a new set of semi-empirical spectrophotometric templates using the DESI data themselves.
\item Figure out how to deal with aperture effects better. 
\item Improved fitting of QSOs.
\end{itemize}


\begin{acknowledgements}
JM gratefully acknowledges funding support for this work from the U.S. Department of Energy, Office of Science, Office of High Energy Physics under Award Number DE-SC0020086.

This research is supported by the Director, Office of Science, Office of High Energy Physics of the U.S. Department of Energy under Contract No. DE–AC02–05CH11231, and by the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility under the same contract; additional support for DESI is provided by the U.S. National Science Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to the NSF’s National Optical-Infrared Astronomy Research Laboratory; the Science and Technologies Facilities Council of the United Kingdom; the Gordon and Betty Moore Foundation; the Heising-Simons Foundation; the French Alternative Energies and Atomic Energy Commission (CEA); the National Council of Science and Technology of Mexico; the Ministry of Economy of Spain, and by the DESI Member Institutions.

The authors are honored to be permitted to conduct scientific research on Iolkam Du’ag (Kitt Peak), a mountain with particular significance to the Tohono O’odham Nation.

\end{acknowledgements}

\begin{appendix}

Building the SPS models:

\begin{verbose}
FFLAGS="-DMILES=0 -DC3K=1" python -m pip install fsps --no-binary fsps
\end{verbose}


\end{appendix}


\bibliographystyle{aasjournal}
\bibliography{bib}

\end{document}
